Rationality, Evolution \& the Environment

### 2015-08-21 paper/paper.tex
minor edits

\begin{itemize}
\item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
  type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
\item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
  and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
  actually shows something stronger, namely strict dominance, but everything is formulated in
  terms of stability; using dominance is also better for arguments about evolutionary dynamics:
  dynamics can be attracted by states that are not evolutionarily stable (even if there is an
  ESS), but dominated strategies will die out in any case;
\item should we give definitions for ESS and NSS in the main text?
\item should we include definitions of the replicator dynamic and/or the replicator mutator
  dynamic?
\item the most important issue with this text is still that we need to motivate why we care
  about non-probabilistic beliefs and/or security strategies; everything else will fall into
  place when that is done
\end{itemize}

@@

But this is orthogonal to the arguments in this paper, where the focus is on possibilities for
the evolution of non-veridical preferences. We know from Fact~\ref{fact:maxEU-minReg} that
regret types and veridical preference types, when paired with probabilistic belief types that
maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they belief},
as long as they belief the same. So, if learning, insight and statistical knowledge of a
recurrent situation \emph{can} be brought to bear, this will not make evolution select against
regret-based preferences. If, on the other hand, agents have no basis for probabilistic
beliefs, then we have shown that there are general and basic circumstances in which
regret-based preferences can actually be selected, despite their non-veridicality.

>>>>

\begin{itemize}
\item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
  type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
\item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
  and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
  actually shows something stronger, namely strict dominance, but everything is formulated in
  terms of stability; using dominance is also better for arguments about evolutionary dynamics:
  dynamics can be attracted by states that are not evolutionarily stable (even if there is an
  ESS), but dominated strategies will die out in any case;
\item should we give definitions for ESS and NSS in the main text?
\item should we include definitions of the replicator dynamic and/or the replicator mutator
  dynamic?
\item the most important issue with this text is still that we need to motivate why we care
  about non-probabilistic beliefs and/or security strategies; everything else will fall into
  place when that is done
\item an important ingredient in our argument pro regret is that radical uncertainty could be
  exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
  ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
\item a major contribution of our paper is the ``meta-game'' approach, but in the current
  version I feel that this is not stressed sufficiently; the introduction and the beginning of
  section 3 could do a bit more to carve out this idea as something generally cool; especially
  the formula from 3.4 could occur earlier (albeit in more general notation);
\end{itemize}

@@

But this is orthogonal to the arguments in this paper, where the focus is on possibilities for
the evolution of non-veridical preferences. We know from Fact~\ref{fact:maxEU-minReg} that
regret types and veridical preference types, when paired with probabilistic belief types that
maximize/minimize expectations, are behaviorally equivalent, \emph{no matter what they believe},
as long as they belief the same. So, if learning, insight and statistical knowledge of a
recurrent situation \emph{can} be brought to bear, this will not make evolution select against
regret-based preferences. If, on the other hand, agents have no basis for probabilistic
beliefs, then we have shown that there are general and basic circumstances in which
regret-based preferences can actually be selected, despite their non-veridicality.
